working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect

### 2019-03-04 Manuscript_draft/Manuscript_draft.Rmd
edits

\newpage
```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, out.width='100%', fig.cap="A"}
knitr::include_graphics('images/phylo_image.png')
```

>>>>

\newpage
```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, out.width='100%', fig.cap="Phylogenetic tree of the ten species used in the experiment from three different families from bottom to top: Solanaceae, Convolvulaceae and Brassicaceae."}
knitr::include_graphics('images/phylo_image.png')
```
